The \dealii Library, Version 9.5

### 2023-06-16 9.5/paper.tex
add text for Intersected meshes section

\subsubsection{Intersected meshes}

\todo[inline]{Complete.}

\begin{itemize}
\item uses \texttt{CGAL}~\cite{cgal-user-ref}
\item data can be used to fill \texttt{RemotePointEvaluation} (communication-free)
\item used successfully in \cite{heinz2023high} to perform Nitsche-type mortaring in the context
of the conservative formulation of acoustic equations discretized with
DG, in order to suppress artificial modes
\end{itemize}

\subsubsection{Non-nested multigrid}

@@

>>>>

\subsubsection{Intersected meshes}
In the current release, we added experimental support to compute intersections on parallel::distributed::Triangulation objects using \texttt{CGAL}~\cite{cgal-user-ref}.
For this purpose we introduced a free function which computes intersections and relevant information for communication from \texttt{intersection\_requests}.
\texttt{intersection\_requests} is a vector that contains entities for which intersections are computed on a given triangulation (in the form of \texttt{GridTools::Cache}).
Each entity (faces or cells) is described by a vector of vertices.

\begin{c++}
// compute intersections on distributed triangulation  
auto intersection_data =
       GridTools::internal::distributed_compute_intersection_locations(
         cache, intersection_requests, global_bboxes, marked_vertices,
         tolerance);
\end{c++}

For the common case of Nitsche-type mortaring, quadrature points must be distributed on the intersections where relevant quantities are evaluated.
The \texttt{intersection\_data} returned by the function above can convert itself to data which can be used to fill \texttt{RemotePointEvaluation}.
The whole procedure is done communication-free.

\begin{c++}
// distribute n_points_1D quadrature points to the intersections
auto point_data = intersection_data.template 
       convert_to_distributed_compute_point_locations_internal<dim>(
         n_points_1D, tria, mapping,
         // following parameter is optional would need additional
         // communication 
         consistent_numbering_of_sender_and_receiver);

// use point_data to reinit RemotePointEvaluation
Utilities::MPI::RemotePointEvaluation<dim> rpe;
rpe.reinit(point_data,tria, mapping);
\end{c++}

This functionality is handy since \texttt{RemotePointEvaluation} can now be used to access quantities in quadrature points on intersections without further ado.
To reduce the user's effort, we plan to add a wrapper that takes care of the described procedure and provides interfaces like \texttt{FEEvaluation} to access quantities easily, e.g., in a matrix-free loop.

Described implementation and an early version of the wrapper have been used successfully in~\cite{heinz2023high} to perform Nitsche-type mortaring in the context of the conservative formulation of acoustic equations discretized with DG to suppress artificial modes.
\subsubsection{Non-nested multigrid}

@@

M.~Bergbauer was supported by the German Research Foundation (DFG) 
under the project ``High-Performance Cut Discontinuous Galerkin Methods
for Flow Problems and Surface-Coupled Multiphysics Problems''.
